Bayesian Sparsification of Deep $\cplx$-valued networks

### 2020-01-31 paper/paper.tex
fleshed out placeholder figures

\begin{figure}[!ht]
  \centering
  \begin{subfigure}[b]{0.9\textwidth}  % imcl2019-style swears at this
    \centering
    \includegraphics[width=1.\linewidth,draft]{../assets/log-alpha__histograms.pdf}
    % \caption{} \label{fig:log-relevance-kde}
  \end{subfigure} \\
  % \hfill
  \begin{subfigure}[b]{0.9\textwidth}  % imcl2019-style swears at this
    \centering
    \includegraphics[width=1.\linewidth,draft]{../assets/proba_of_nonzero.pdf}
    % \caption{} \label{fig:log-relevance-proba}
  \end{subfigure}
  \caption{%
    \textit{top}: Estimate of $\log\alpha$ density for a convolutional and dense layer
    from the convolutional model of sec.~\ref{sub:mnist_like_datasets}.
    \textit{bottom}: The probability of a parameter being within $\pm \delta$ relative
    tolerance of its mean.
  }
  \label{fig:log-relevance}
\end{figure}

@@

% a couple of plots from MNIST and Fashion-MNIST
\begin{figure}[!ht]
  \centering
  \begin{subfigure}[b]{0.9\textwidth}  % imcl2019-style swears at this
    \centering
    \includegraphics[width=1.\linewidth,draft]{../assets/log-alpha__histograms.pdf}
    % \caption{} \label{fig:log-relevance-kde}
  \end{subfigure} \\
  % \hfill
  \begin{subfigure}[b]{0.9\textwidth}  % imcl2019-style swears at this
    \centering
    \includegraphics[width=1.\linewidth,draft]{../assets/proba_of_nonzero.pdf}
    % \caption{} \label{fig:log-relevance-proba}
  \end{subfigure}
  \caption{%
    \textit{top}: The performance-compression tradeoff for MNIST \citep{citation_needed}.
    \textit{bottom}: The performance-compression tradeoff for Fashion MNIST \citep{citation_needed}.
  }
  \label{fig:mnist-like_tradeoff}
\end{figure}

@@

\begin{figure}[!ht]
  \centering
  \begin{subfigure}[b]{0.9\textwidth}  % imcl2019-style swears at this
    \centering
    \includegraphics[width=1.\linewidth,draft]{../assets/log-alpha__histograms.pdf}
    % \caption{} \label{fig:log-relevance-kde}
  \end{subfigure} \\
  % \hfill
  \begin{subfigure}[b]{0.9\textwidth}  % imcl2019-style swears at this
    \centering
    \includegraphics[width=1.\linewidth,draft]{../assets/proba_of_nonzero.pdf}
    % \caption{} \label{fig:log-relevance-proba}
  \end{subfigure}
  \caption{%
    \textit{top}: MusicNet for the model of \citep{trabelsi_deep_2017} with kernel size $3$.
    \textit{bottom}: The performance-compression tradeoff for Fashion MNIST \citep{citation_needed}.
  }
  \label{fig:mnist-like_tradeoff}
\end{figure}

% subsection muscinet (end)

>>>>

\begin{figure}[!ht]
  \centering
  \begin{subfigure}[b]{0.9\textwidth}  % imcl2019-style swears at this
    \centering
    \includegraphics[width=1.\linewidth]{../assets/log-alpha__sum__mnist__20200131-202713.pdf}
    % \caption{} \label{fig:log-relevance-kde}
  \end{subfigure} \\
  % \hfill
  \begin{subfigure}[b]{0.9\textwidth}  % imcl2019-style swears at this
    \centering
    \includegraphics[width=1.\linewidth]{../assets/log-alpha__sum__fashion-mnist__20200131-205926.pdf}
    % \caption{} \label{fig:log-relevance-proba}
  \end{subfigure}
  \caption{%
    \textit{top}: Estimate of $\log\alpha$ density for a convolutional and dense layer
    from the convolutional model of sec.~\ref{sub:mnist_like_datasets}.
    \textit{bottom}: The probability of a parameter being within $\pm \delta$ relative
    tolerance of its mean.
  }
  \label{fig:log-relevance}
\end{figure}

@@

% a couple of plots from MNIST and Fashion-MNIST
\begin{figure}[!ht]
  \centering
  \begin{subfigure}[b]{0.95\textwidth}  % imcl2019-style swears at this
    \centering
    \includegraphics[width=1.\linewidth]{../assets/sum__mnist__fine-tune.pdf}
    % \caption{} \label{fig:log-relevance-kde}
  \end{subfigure} \\%
  % \hfill
  \begin{subfigure}[b]{0.95\textwidth}  % imcl2019-style swears at this
    \centering
    \includegraphics[width=1.\linewidth]{../assets/sum__fashion-mnist__fine-tune.pdf}
    % \caption{} \label{fig:log-relevance-proba}
  \end{subfigure}
  \caption{%
    The accuracy-compression tradeoff after ``fine-tune''.
    \textit{top}: MNIST \citep{citation_needed};
    \textit{bottom}: Fashion MNIST \citep{citation_needed}.
  }
  \label{fig:mnist-like_tradeoff}
\end{figure}

@@

\begin{figure}[!ht]
  \centering
  \begin{subfigure}[b]{0.9\textwidth}  % imcl2019-style swears at this
    \centering
    \includegraphics[width=1.\linewidth]{../assets/grid_cplx_fine_kl_div_v3_fast-fine-tune.pdf}
    % \caption{} \label{fig:log-relevance-kde}
  \end{subfigure} \\
  % \hfill
  \begin{subfigure}[b]{0.9\textwidth}  % imcl2019-style swears at this
    \centering
    \includegraphics[width=1.\linewidth]{../assets/grid_cplx_fine_kl_div_v2-fine-tune.pdf}
    % \caption{} \label{fig:log-relevance-proba}
  \end{subfigure}
  \caption{%
    Average Percision frontier for the convolutional model of \citet{trabelsi_deep_2017}.
    Shaded horiontal region represents the $\mu\pm\sigma$ bands for the performance of the
    uncompressed model.
    \textit{top}: Original model ($k=6$) compressed with \textbf{\color{orange} VD}
    (\ref{ssub:variational_dropout}) and \textbf{\color{blue} ARD} (\ref{ssub:empirical_bayes});
    \textit{bottom}: The model of \citep{trabelsi_deep_2017} with kernel size $3$
    compressed with \textbf{\color{blue} VD} (\ref{ssub:variational_dropout}).
  }
  \label{fig:musicnet_tradeoff}
\end{figure}

\begin{figure}[!ht]
  \centering
  \begin{subfigure}[b]{0.9\textwidth}  % imcl2019-style swears at this
    \centering
    \includegraphics[width=1.\linewidth]{../assets/grid_cplx_fine_kl_div_v3_fast-c-ard-tradeoff.pdf}
    % \caption{} \label{fig:log-relevance-kde}
  \end{subfigure} \\
  % \hfill
  \begin{subfigure}[b]{0.9\textwidth}  % imcl2019-style swears at this
    \centering
    \includegraphics[width=1.\linewidth]{../assets/grid_cplx_fine_kl_div_v3_fast-c-ard-tradeoff.pdf}
    % \caption{} \label{fig:log-relevance-proba}
  \end{subfigure}
  \caption{%
    Pre ``finte-tune'' performance of the best models from figure \ref{fig:musicnet_tradeoff}
    compressed with methods of sec.~\ref{sec:dropout_for_c_valued_layers}:
    (\ref{ssub:variational_dropout} -- \textit{top}, \ref{ssub:empirical_bayes} --  \textit{bottom}).
  }
  \label{fig:musicnet_tradeoff_pre_fune-tune}
\end{figure}
% subsection muscinet (end)
